Machine Learning Methods for Site-specific Input Management

### 2022-02-10 Codes/PrepareResults.rmd
Organize codes

## Profit loss summary and distributions
```{r}
piLoss_density <-
  copy(res_allML) %>%
  .[, Method := case_when(
    Method == "CF_base" ~ "CF-base",
    Method == "RF" ~ "RF",
    Method == "BRF" ~ "BRF",
    Method == "CNN" ~ "CNN"
  )] %>%
  .[, Model := case_when(
    Model == "aby" ~ "Scenario: aby",
    Model == "abytt" ~ "Scenario: abytt",
    Model == "aabbyy" ~ "Scenario: aabbyy",
    Model == "aabbyytt" ~ "Scenario: aabbyytt"
  )] %>%
  .[, Method := factor(Method, levels = c("RF", "BRF", "CNN", "CF-base"))] %>%
  .[, Model := factor(Model,
    levels = c("Scenario: aby", "Scenario: abytt", "Scenario: aabbyy", "Scenario: aabbyytt")
  )] %>%
  ggplot() +
  geom_density(aes(x = Mean, fill = Method), alpha = 0.7) +
  # scale_fill_viridis(discrete = TRUE, alpha=0.5) +
  # scale_fill_viridis_d()+
  labs(x = expression(paste(hat(pi)["loss"], " ($/ha)"))) +
  # labs(x = TeX("$\\hat{pi}_{loss}$ (\\$/ha)")) +
  facet_wrap(~Model, ncol = 1) +
  theme_dist

>>>>

## Profit loss summary and distributions
```{r}
piLoss_density <-
  copy(res_allML) %>%
  .[, Method := case_when(
    Method == "CF_base" ~ "CF-base",
    Method == "RF" ~ "RF",
    Method == "BRF" ~ "BRF",
    Method == "CNN" ~ "CNN"
  )] %>%
  .[, Model := case_when(
    Model == "aby" ~ "Scenario: aby",
    Model == "abytt" ~ "Scenario: abytt",
    Model == "aabbyy" ~ "Scenario: aabbyy",
    Model == "aabbyytt" ~ "Scenario: aabbyytt"
  )] %>%
  .[, Method := factor(Method, levels = c("RF", "BRF", "CNN", "CF-base"))] %>%
  .[, Model := factor(Model,
    levels = c("Scenario: aby", "Scenario: abytt", "Scenario: aabbyy", "Scenario: aabbyytt")
  )] %>%
  ggplot() +
  geom_density(aes(x = Mean, fill = Method), alpha = 0.7) +
  # scale_fill_viridis(discrete = TRUE, alpha=0.5) +
  # scale_fill_viridis_d()+
  labs(x = expression(paste(hat(pi)["def"], " ($/ha)"))) +
  facet_wrap(~Model, ncol = 1) +
  theme_dist
